\input{title.tex}

### 2022-07-04 docs/papers/01_manuscript/03_results.tex
fix(rectify-by-shuaiwang-comment): fix case1-case3 in order
BREAKING CHANGE:

For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management (case 3), each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water (case 2), leading to higher water use than that of the past decentralized situation (case 1).
Furthermore, in case 2, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.

>>>>

For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\nameref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.

### 2022-07-04 docs/papers/01_manuscript/06_methods.tex
fix(rectify-by-shuaiwang-comment): fix case1-case3 in order
BREAKING CHANGE:

Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

>>>>

Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}~C), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2022-07-04 docs/papers/02_appendix/04_theoretical_model.tex
fix(rectify-by-shuaiwang-comment): fix case1-case3 in order
BREAKING CHANGE:

 %case1
\begin{case}Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.

@@

 %case2
 \begin{case} Mismatched decision: This case corresponds to a mismatched institution.

>>>>

 %case1
\begin{case} Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.

@@

 %case2
 \begin{case} Mismatched institution: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.
